%\thesistitlepage % make the ordinary titlepage
\hypersetup{pageanchor=false}
%\include{summary}

\chapter*{Preface}

%Here, you give a brief introduction to your work. What it is (e.g., a Master's thesis in AIMT at NTNU, when it was carried out (e.g., during the autumn semester of 2021). If the project has been carried out with a company, you should mention this and also describe the cooperation with the company. You may also describe how the idea to the project was brought up.

%You should also specify the assumed background of the readers of this report (who are you writing for).\\[2cm]

This Master's thesis was written in conjunction with a part-time Master program in Interaction Design at the Faculty of Architecture and Design at Norwegian University of Science and Technology, campus Gjøvik.\\%[1cm]

My motivation for this master thesis is a result of a long standing passion for free-hand gesture interaction. Science fiction movie such as Iron Man or Minority Report inspired me and envisioned a new and exciting field in Human Computer Interaction.\\


I would like to thank my supervisor from NTNU Gjøvik, prof. Frode Volden, for his patience and great help during my master thesis. His expertise and feedback was crucial for the final result.\\

Furthermore, I would like to thank all the parents who let me run the ability test on their children. Thank you for your cooperation and faith in my project. 
Also, I would like to thank the pediatrician, who, unfortunately, would liked to be anonymous,  for the short notice interview. I appreciate her opinion about the concept.\\

Additionally, I would like to thank Devinco, the company who I am currently employed, for being understanding and supportive. I hope, I can contribute with useful ideas and expertise for all my future work. Special thanks goes to Tore Sævik, head of department, for implanting the crazy idea to apply for higher education. Moreover, my dear colleagues, thank you for all your support, motivation and help I got during the writing of my master thesis. \\

Last but not least, I would like to thank my closest friends, my family and especially my boyfriend for being so understanding for my all to0 often absence and listing to all my whining and frustration in the last months. Thank you for believing in me and for all the motivation and contributions I have gotten. It was a hard and long journey and I am happy to finally have reached the goal. \\[2cm]


%\begin{center}
%\thesiscampus, 
\begin{flushright}

\thesisdate \\[1pc]
S.G.\\[1pc]
\end{flushright}
%\thesisauthor
%\end{center}